---
output: md_document
---
| \-\-\-
| title: Employment in STEM
| date: 2021-01-01
| type: post
| weight: 300
| summary: "Female employment in STEM (%)"
| \-\-\-


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
# Libraries
library(kableExtra)

```

```{r include=FALSE}
# Create dataframe
df_employment <- read.csv("../../CSVs/employment_rates_test1.csv")

```

# Employment rates 3

````{verbatim}
{{< details "More information" >}}
The details component allows you to hide more detailed information 
that might be relevant to only some users.
{{< /details >}}
````


```{escape=FALSE}
{{< details "More information" >}}
The details component allows you to hide more detailed information 
that might be relevant to only some users.
{{< /details >}}
```


| {{\< details "More information" \>}}
| The details component allows you to hide more detailed information 
| that might be relevant to only some users.
| {{< /details >}}

| {{< tabset >}}
| {{< tab title="First Tab" >}}
| My first tab
| {{< /tab >}}
| {{< tab title="Tab 2" >}}
| My second tab
| {{< /tab >}}
| {{< tab title="Third" >}}
| My third tab
| {{< /tab >}}
| {{< /tabset >}}

## The female employment rate was 72.1% in May 2023

Female and male employment rates in the UK (aged 16 to 64, seasonally adjusted)

## Employment rates, January 2020 to May 2023

```{r echo=FALSE}
knitr::kable(read.csv("../../CSVs/employment_rates_test1.csv"),)
```
